Unrecognized States: A Theory of Self-Determination and Foreign Influence

### 2015-09-01 draft.tex
modify lemmas 3 and 4 for homogenized delta

\item  \textit{$\frac {-\nu\cdot p_{1s}}{1-\delta_c} \geq \frac{\lambda \cdot p_{1s} + \mu}{1 -\de_p} + \frac{\beta}{1 -\de_c}$: recognition of the secessionist state is more important for the international community to avoid than for the patron to achieve.}

@@

Thus the difference in continuation values from switching from the status quo to recognition for player $p$ is $\frac{\lambda +R_p^{SQ}}{1 -\de_p} -R_p^{REC}$. For player $c$ it is $\frac{\nu + R_c^{SQ}}{1 -\de_c}-R_c^{REC}$. As noted above, $R_c^{REC} =0$. So $c$ is willing to invest up to $-\nu$ per period toward maintaining the status quo, and $p$ is willing to invest up to $\frac{\lambda +R_p^{SQ}}{1 -\de_p}$ toward recognition. We have shown that the largest possible investments by $p$ in the status quo are $\frac{\beta}{1 -\de_c}$ in $n=1$ and $\mu$ in each period thereafter, so the largest this difference can be for $p$ is $\frac{\lambda + \mu}{1 -\de_p} + \frac{\beta}{1 -\de_c}$.

@@

Given our assumption that the status quo outcome is no worse than the recognition outcome net of investments for player $g$, $p$'s willingness to invest up to $\frac{\lambda + \mu}{1 -\de_p} + \frac{\beta}{1 -\de_c}$ can create a difference of at most that amount in $L_{gn} - q_{gn}$.

Thus $\frac{-\nu}{1 -\de_c} > \frac{\lambda + \mu}{1 -\de_p} + \frac{\beta}{1 -\de_c}$ guarantees that player $c$ will always be willing to counter an investment by player $p$ toward achieving recognition, making $p$ unwilling to make that investment in the initial stage and making the response by player $c$ unnecessary. A slightly weaker version of this inequality is stated as condition 4 so that this deterrence dynamic is guaranteed to operate through the war lottery as well, as will be seen in Lemma 4. \hfill $\blacksquare$
\\
\\
\noindent {\bf Proof of Lemma 4} \\
The difference in continuation values from switching from the status quo to taking the war lottery for player $p$ is $\frac{\lambda p_1 + \alpha p_2 }{1 -\de_p} +R_p^{SQ} -R_p^{WAR}$. For player $c$ it is $\frac{\nu p_1 + \beta p_2}{1 -\de_c} + R_c^{SQ} -R_c^{WAR}$. As noted above, $R_c^{SQ} =0$. So $c$ is willing to invest up to $\frac{\nu p_1 + \beta p_2}{1 -\de_c}$ toward preventing fighting if this quantity is negative (leave the case where it is non-negative until later).

$p$ is willing to invest up to $\frac{\lambda p_1 + \alpha p_2 }{1 -\de_p} +R_p^{SQ}$ toward instigating fighting when this quantity is positive, and will not invest when the quantity is non-positive. Thus we must only examine the case where this quantity is positive.

We will again set $R_p^{SQ}$ at its largest value of $\frac{\mu}{1-\de_p} + \frac{\beta}{1 - \de_c}$ as this is most restrictive. In this only case of interest, we have $\frac{\alpha p_2}{1 -\de_p} +\frac{\lambda p_1}{1 -\de_p} + \frac{\mu}{1-\de_p} + \frac{\beta}{1 - \de_c}> 0$. Note that the first term is negative while the rest are positive.

Multiplying Condition 3 by $-p_{2s}$, we have $\frac{-\beta \cdot p_{2s}}{1-\de_c} \geq \frac{\alpha \cdot p_{2s}}{1-\de_p}$. Using this with Condition 4, we have
\[
  \textstyle -\left(\frac{\nu p_{1s} + \beta p_{2s}}{1 -\de_c}\right) = - \frac{\nu p_{1s}}{1 -\de_c} - \frac{\beta p_{2s}}{1 -\de_c} \geq \frac{\alpha p_{2s}}{1 -\de_p} +\frac{\lambda p_{1s}}{1 -\de_p} + \frac{\mu}{1-\de_p} + \frac{\beta}{1 - \de_c}> 0 \ \forall p_{1s},p_{2s}
\]

>>>>

\item  \textit{$-\nu\cdot p_{1s} \geq \lambda \cdot p_{1s} + \mu + \beta$: recognition of the secessionist state is more important for the international community to avoid than for the patron to achieve.}

@@

Thus the difference in continuation values from switching from the status quo to recognition for player $p$ is $\frac{\lambda +R_p^{SQ}}{1 -\de} -R_p^{REC}$. For player $c$ it is $\frac{\nu + R_c^{SQ}}{1 -\de}-R_c^{REC}$. As noted above, $R_c^{REC} =0$. So $c$ is willing to invest up to $-\nu$ per period toward maintaining the status quo, and $p$ is willing to invest up to $\frac{\lambda +R_p^{SQ}}{1 -\de}$ toward recognition. We have shown that the largest possible investments by $p$ in the status quo are $\frac{\beta}{1 -\de}$ in $n=1$ and $\mu$ in each period thereafter, so the largest this difference can be for $p$ is $\frac{\lambda + \mu + \beta}{1 -\de}$.

@@

Given our assumption that the status quo outcome is no worse than the recognition outcome net of investments for player $g$, $p$'s willingness to invest up to $\frac{\lambda + \mu + \beta}{1 -\de}$ can create a difference of at most that amount in $L_{gn} - q_{gn}$.

Thus $\frac{-\nu}{1 -\de} > \frac{\lambda + \mu + \beta}{1 -\de}$ guarantees that player $c$ will always be willing to counter an investment by player $p$ toward achieving recognition, making $p$ unwilling to make that investment in the initial stage and making the response by player $c$ unnecessary. A slightly weaker version of this inequality is stated as condition 4 so that this deterrence dynamic is guaranteed to operate through the war lottery as well, as will be seen in Lemma 4. \hfill $\blacksquare$
\\
\\
\noindent {\bf Proof of Lemma 4} \\
The difference in continuation values from switching from the status quo to taking the war lottery for player $p$ is $\frac{\lambda p_1 + \alpha p_2 }{1 -\de} +R_p^{SQ} -R_p^{WAR}$. For player $c$ it is $\frac{\nu p_1 + \beta p_2}{1 -\de} + R_c^{SQ} -R_c^{WAR}$. As noted above, $R_c^{SQ} =0$. So $c$ is willing to invest up to $\frac{\nu p_1 + \beta p_2}{1 -\de}$ toward preventing fighting if this quantity is negative (leave the case where it is non-negative until later).

$p$ is willing to invest up to $\frac{\lambda p_1 + \alpha p_2 }{1 -\de} +R_p^{SQ}$ toward instigating fighting when this quantity is positive, and will not invest when the quantity is non-positive. Thus we must only examine the case where this quantity is positive.

We will again set $R_p^{SQ}$ at its largest value of $\frac{\mu + \beta}{1-\de}$ as this is most restrictive. In this only case of interest, we have $\frac{\alpha p_2 + \lambda p_1 + \mu + \beta}{1 - \de}> 0$. Note that the first term is negative while the rest are positive.

Multiplying Condition 3 by $-p_{2s}$, we have $-\beta \cdot p_{2s} \geq \alpha \cdot p_{2s}$. Using this with Condition 4, we have $- \nu p_{1s} - \beta p_{2s} \geq \alpha p_{2s} +\lambda p_{1s} + \mu + \beta> 0 \ \forall p_{1s},p_{2s}$ and therefore also
\[
  \textstyle -\left(\frac{\nu p_{1s} + \beta p_{2s}}{1 -\de}\right) \geq \frac{\alpha p_{2s}+ \lambda p_{1s} + \mu + \beta}{1 - \de}> 0 \ \forall p_{1s},p_{2s}
\]
